---
output:
  html_document:
    toc: no
    toc_depth: 6
    toc_float:
      collapsed: yes
    fig_width: 7
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

<style type="text/css">
div.main-container {
  max-width: 2000px;
  margin-left: 0;
  margin-right: auto;
}
</style>

<style>
.tocify {
color: black;
}
<!-- } -->
<!-- .tocify .tocify-header { -->
<!--     position: fixed; -->
<!--     <!-- top: 50px; --> -->
<!--     left: 50px; -->
<!--     width: 350px; -->
<!--     <!-- border: solid 3px black; --> -->
<!--     <!-- height: 200px; --> -->
<!--  border: none; -->
<!-- } -->
.tocify .tocify-header .active {
color: white;
background: #d80b8c;
font-weight: bold;
}
<!-- .tocify .tocify-item { -->
<!-- background: white; -->
<!-- color: black; -->
<!--  border: none; -->
<!-- } -->
</style>


<style>
  .nav-pills>li>a:hover, .nav-pills>li>a:focus, .nav-pills>li.active>a,     .nav-pills>li.active>a:hover, .nav-pills>li.active>a:focus{
     background-color: #212070;
     }
</style>

<style>
.container { width: 1800px; }
h2 {
  background-color: #dddedd;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h3 {
  background-color: #f2f2f2;
  color: black;
  text-indent: 20px;
  <!-- font-weight: bold; -->
}
h4 {
  <!-- background-color: #dddedd; -->
  <!-- color: black; -->
  text-indent: 50px;
  <!-- font-weight: bold; -->
}
</style>

<style>
.blackbox {
  padding: 1em;
  background: white;
  color: black;
  border: 2px solid #7f7f7f;
  width: 100%;
  position: center;
  align: center;
  margin: 0px auto;
}
.center {
  text-align: left;
  margin: 0px auto;
}
</style>


<!-- ```{css toc-content, echo = FALSE} -->
<!-- #TOC { -->
<!--   right: 270px; -->
<!--   margin: 20px 0px 25px 0px; -->
<!-- } -->

<!-- .main-container { -->
<!--     margin-left: 200px; -->
<!-- } -->
<!-- ``` -->


```{r Load Packages, echo = FALSE, warning = FALSE, message = FALSE}
# # Load packages -----------------------------------------------------------------------------------
suppressMessages({
  memory.limit(size = 8000000)
  library(readxl)
  library(writexl)
  library(plyr)
  library(dplyr)
  library(data.table)
  library(zoo)
  library(shiny)
  library(shinydashboard)
  library(shinydashboardPlus)
  library(shinyWidgets)
  library(htmlwidgets)
  library(lubridate)
  library(tcltk)
  library(tidyverse)
  library(plotly)
  library(knitr)
  library(kableExtra)
  library(leaflet)
  library(grid)
  library(gridExtra)
  library(eeptools)
  library(ggQC)
  library(zipcodeR)
  library(utils)
  library(scales)
  library(chron)
  library(bupaR)
  library(shiny)
  library(DT)
  library(DiagrammeR)
  library(shinyalert)
  library(edeaR)
  library(processmapR)
  library(processmonitR)
  library(processanimateR)
  library(tidyr)
  library(lubridate)
  library(RColorBrewer)
  library(DiagrammeR)
  library(ggplot2)
  library(leaflet)
  library(readr)
  library(highcharter)
  library(ggforce) # for 'geom_arc_bar'
  library(packcircles) # for packed circle graph
  library(viridis)
  library(ggiraph)
  library(treemapify)
  library(treemap)
  library(broom)
  library(extrafont)
  library(tis) # for US holidays
  library(vroom)
  library(sjmisc)
  library(tools)
  library(here)
  library(shinyBS)
  library(shinyscreenshot)
  library(fasttime)
  library(shinycssloaders)
  library(feather)
  # library(zipcodeR)
  library(formattable)
  library(shinyjs)
  library(janitor)
  library(patchwork)
  library(flexdashboard)
  # library(tidyverse)
  # library(viridis)
  # library(hrbrthemes)
  # library(plotly)
  # install.packages("bsts")
  library(bsts)
  library(reactable)
  # install.packages("reactablefmtr")
  library(reactablefmtr)
  library(svDialogs)
  # library(openxlsx)
  library(flextable)
  library(officedown)
  library(officer)
  library(magrittr)
  library(webshot) 
  library(png)
  library(ggh4x)
  library(RODBC)
  library(DBI)
  library(odbc)
  library(dbplyr)
  library(pool)
  library(emojifont)
})

```


```{r Graph asthetics, echo = FALSE, warning = FALSE, message = FALSE}
### Color Functions for Graphs ============================================================
# Mount Sinai corporate colors "USE THIS TO ADD COLORS"
MountSinai_colors <- c(
  `dark purple`  = "#212070",
  `dark pink`    = "#d80b8c",
  `dark blue`    = "#00aeef",
  `dark grey`    = "#7f7f7f",
  `yellow`       = "#ffc000",
  `purple`       = "#7030a0",
  `med purple`   = "#5753d0",
  `med pink`     = "#f75dbe",
  `med blue`     = "#5cd3ff",
  `med grey`     = "#a5a7a5",
  `light purple` = "#c7c6ef",
  `light pink`   = "#fcc9e9",
  `light blue`   = "#c9f0ff",
  `light grey`   = "#dddedd"
  )
# Function to extract Mount Sinai colors as hex codes
# Use Character names of MountSinai_colors
MountSinai_cols <- function(...) {
  cols <- c(...)
  
  if (is.null(cols))
    return (MountSinai_colors)
  
  MountSinai_colors[cols]
}
# Color Function that can be used to call all colors is "MountSinai_cols()"
# Use in ggplot 
  #MountSinai_cols()       # will provide all colors and their hex codes in a table 
  #MountSinai_cols("pink") # will provide color name and the hex code for the pink color
# Create palettes 
MountSinai_palettes <- list(
  `all`   = MountSinai_cols("dark purple","dark pink","dark blue","dark grey",
                            "med purple","med pink","med blue","med grey", 
                            "light purple","light pink","light blue","light grey"),
  
  `main`  = MountSinai_cols("dark purple","dark pink","dark blue","dark grey"),
  
  `purple`  = MountSinai_cols("dark purple","med purple","light purple"),
  
  `pink`  = MountSinai_cols("dark pink","med pink","light pink"),
  
  `blue`  = MountSinai_cols("dark blue", "med blue", "light blue"),
  
  `grey`  = MountSinai_cols("dark grey", "med grey", "light grey"),
  
  `purpleGrey` = MountSinai_cols("dark purple", "dark grey"),
  
  `pinkBlue` = MountSinai_cols("dark pink", "dark blue")
  
)
# MountSinai_palettes
# Return function to interpolate a Mount Sinai color palette
# default value is the main palette, reverse = True will change the order
MountSinai_pal <- function(palette = "all", reverse = FALSE, ...) {
  pal <- MountSinai_palettes[[palette]]
  
  if (reverse) pal <- rev(pal)
  
  colorRampPalette(pal, ...)
}
# Scale Function for ggplot can be used instead of scale_color_manual
scale_color_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  
  if (discrete) {
    discrete_scale("colour", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_color_gradientn(colours = pal(256), ...)
  }
}
# Scale Fill for ggplot insetead of scale_fill_manual 
scale_fill_MountSinai <- function(palette = "all", discrete = TRUE, reverse = FALSE, ...) {
  pal <- MountSinai_pal(palette = palette, reverse = reverse)
  if (discrete) {
    discrete_scale("fill", paste0("MountSinai_", palette), palette = pal, ...)
  } else {
    scale_fill_gradientn(colours = pal(256), ...)
  }
}
# Use in ggplot 
  # scale_color_MountSinai("main")
```


```{r Global Variables, echo = FALSE, warning = FALSE, message = FALSE}

'%!in%' <- function(x,y)!('%in%'(x,y))

```


```{r Establish Connection, echo = FALSE, warning = FALSE, message = FALSE}

# Connection to Oracle DB ------------------------------------------------------
# conn1 <- dbPool(drv = odbc(), dsn = "OAO Cloud DB SoYoun", timeout = 30)

conn1 <- dbConnect(odbc(), "OAO Cloud DB SoYoun", timeout = 30)
conn2 <- dbConnect(odbc(), 
                  "Clarity_prod", 
                  uid = "kweons01" , 
                  pwd = "kweons01123$")


# Connection to Clarity Tables -------------------------------------------------
slot_raw_tbl <- tbl(conn2, "Y_DM_BOOKED_FILLED_RATE")
access_raw_tbl <- tbl(conn2, "MV_DM_PATIENT_ACCESS")
availability_raw_tbl <- tbl(conn2, "V_AVAILABILITY")
block_raw_tbl <- tbl(conn2, "AVAIL_BLOCK")
block_name_tbl <- tbl(conn2, "ZC_APPT_BLOCK")
orders_raw_tbl <- tbl(conn2, "ORDER_PROC")
coverage_tbl <- tbl(conn2, "V_PAT_ENC_COVERAGE")
encounters_tbl <- tbl(conn2, "PAT_ENC")
myChart_tbl <- tbl(conn2, "V_MYC_MESG")
inBasket_tbl <- tbl(conn2, "IB_MESSAGES")
template_tbl <- tbl(conn2, "TEMPLATE")
user_activity_hour_tbl <- tbl(conn2, "UAL_ACTIVITY_HOURS")
user_login_activity_tbl <- tbl(conn2, "V_ACCESS_LOG")
user_access_log_tbl <- tbl(conn2, "ACCESS_LOG")
clarity_ser_tbl <- tbl(conn2, "CLARITY_SER") # Physician Titles
workstation_tbl <- tbl(conn2, "CLARITY_LWS")

# Connection to OAO Tables -----------------------------------------------------
utilization_tbl <-  tbl(conn1, in_schema("VILLEA04", "UTILIZATION_VIEW"))


# loc_name <- access_raw_tbl %>%
#   group_by(LOC_NAME, DEPARTMENT_NAME) %>%
#   summarise(total = n()) %>%
#   collect()


# user_activity_hour_raw <- user_activity_hour_tbl %>%
#   head(10) %>%
#   collect()

# user_login_activity_raw <- user_login_activity_tbl %>%
#   head(10) %>%
#   collect()
# 
# user_access_log_raw <- user_access_log_tbl %>%
#   head(10) %>%
#   collect()
# 
# prov_directory <- clarity_ser_tbl %>%
#   head(1000) %>%
#   collect()
# 
# workstation_raw <- workstation_tbl %>%
#   filter(WORKSTATION_ID %in% workstations) %>%
#   collect()
# 
# access_raw <- access_raw_tbl %>%
#   filter(DEPARTMENT_ID == 8001090) %>%
#   filter(DERIVED_STATUS_DESC == "Arrived") %>%
#   mutate(appt.year = year(APPT_DTTM),
#          appt.month = month(APPT_DTTM)) %>%
#   filter(appt.year == 2023) %>%
#   collect()
# 
# utilization_raw <- utilization_tbl %>%
#   filter(DEPARTMENT_ID == 8001090) %>%
#   collect()

# user_login_merged <- user_login_activity_tbl %>%
#   filter(DEPARTMENT_ID == 8001090) %>%
#   mutate(login_year = year(LOGIN_TIME),
#          login_month = month(LOGIN_TIME)) %>%
#   filter(login_year == 2023) %>%
#   left_join(user_access_log_tbl %>%
#               dplyr::select(ACCESS_TIME, USER_ID, WORKSTATION_ID),
#             by = c("LOGIN_TIME" = "ACCESS_TIME",
#                    "USER_ID" = "USER_ID")) %>%
#   collect()
# 
#  
# user_activity_hour <- user_activity_hour_tbl %>%
#   left_join(access_raw_tbl %>%
#               dplyr::select(PAT_ENC_CSN_ID, DEPARTMENT_ID, DEPARTMENT_NAME, PROV_NAME_WID),
#             by = c("PAT_ENC_CSN_ID")) %>%
#   filter(DEPARTMENT_ID == 8001090) %>%
#   mutate(activity_year = year(ACTIVITY_HOUR_DTTM),
#          activity_month = month(ACTIVITY_HOUR_DTTM)) %>%
#   filter(activity_year == 2023) %>%
#   collect()

```



```{r Report Variables, echo = FALSE, warning = FALSE, message = FALSE}

day_order <- c("Mon","Tue","Wed","Thu","Fri","Sat","Sun")
hour_order <- as.vector(seq(7,20))
visit_capacity_order <- c(paste0("visit_capacity_",4:10))

report_run_date <- Sys.Date()

```


```{r Space Committee Assessment, echo = FALSE, warning = FALSE, message = FALSE}
# Resource Type Mapping --------------------------------------------------------
resource_types <- clarity_ser_tbl %>%
  dplyr::select(PROV_ID, PROV_NAME, PROV_TYPE, CLINICIAN_TITLE) %>%
  collect()

# Utilization Data Pull --------------------------------------------------------
util_data <- utilization_tbl %>%
  filter(UTIL_TYPE == "scheduled") %>%
  filter(VISIT_METHOD == "IN PERSON") %>%
  filter(DEPARTMENT %like% "1000 10TH%") %>%
  collect()

access_data <- access_raw_tbl %>%
  filter(VISIT_METHOD == "IN PERSON") %>%
  filter(DEPARTMENT_NAME %like% "1000 10TH%") %>%
  dplyr::select(PAT_ENC_CSN_ID, VISIT_TYPE, PRC_NAME) %>%
  mutate(PAT_ENC_CSN_ID = as.character(PAT_ENC_CSN_ID)) %>%
  collect()


util_data <- left_join(util_data, access_data)
  

depts <- util_data %>%
  group_by(DEPARTMENT_OLD, VISIT_METHOD) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = VISIT_METHOD,
              values_from = total,
              values_fill = 0) %>%
  mutate(specialty = "NA",
         floor = "NA") 


total_volume <- utilization_tbl %>%
  filter(UTIL_TYPE == "scheduled") %>%
  filter(DEPARTMENT %like% "1000 10TH%") %>%
  mutate(APPT_MONTH = month(APPT_DATE_YEAR)) %>%
  # filter(APPT_MONTH < 11) %>%
  group_by(APPT_YEAR) %>%
  summarise(total = n()) %>%
  collect() 

total_avg_visits_day <- utilization_tbl %>%
  filter(UTIL_TYPE == "scheduled") %>%
  filter(DEPARTMENT %like% "1000 10TH%") %>%
  mutate(APPT_MONTH = month(APPT_DATE_YEAR)) %>%
  # filter(APPT_MONTH < 11) %>%
  group_by(APPT_YEAR, APPT_DATE_YEAR) %>%
  summarise(total = n()) %>%
  group_by(APPT_YEAR) %>%
  summarise(avg_visits = mean(total)) %>%
  collect()


# Map Provider Type ------------------------------------------------------------
util_data$prov_type <- resource_types$PROV_TYPE[match(util_data$PROV_ID, resource_types$PROV_ID)]


# Identify visit types to exclude ----------------------------------------------
visit_types <- util_data %>%
  group_by(VISIT_TYPE, PRC_NAME) %>%
  summarise(total = n()) 

dept_visits_types <- util_data %>%
  group_by(DEPARTMENT_OLD, VISIT_TYPE, PRC_NAME) %>%
  summarise(total = n())
  
```


```{r Space Committee Assessment Criteria, echo = FALSE, warning = FALSE, message = FALSE}
####### Analysis Criteria ########
# 1000 10th Ave -----------------------
visits_exclude <- "VISUAL FIELD|FLUORESCEIN|LASER|INFUSION|TRANSFUSION|PORT FLUSH|PHLEBOTOMY|PUMP|FLUSH"
visit_types_exclude <- "TREATMENT VISIT"
depts_exclude <- c("1000 10TH FETAL EVAL CLINIC", # Uses separate Sono and NST Rooms
                   "1000 10TH AVE CVI CARDIOLOGY ECHO", # Uses separate Testing, Nuclear Control, Injection, Camera, Lab Rooms
                   "1000 10TH AVE CVI CARDIOLOGY HOLTER",
                   "1000 10TH AVE CVI CARDIOLOGY NUCLEAR",
                   "1000 10TH AVE CVI CARDIOLOGY VASCULAR",
                   "MSW 1000 10TH AVE CARDIOLOGY CT",
                   "1000 10TH AVE EP",
                   "1000 10TH ECHO",
                   "1000 10TH AVE WINSTON 9C ADDICTIONS EVALUATION",
                   "1000 10TH AVE WINSTON 9C ADDICTIONS OUTPATIENT",
                   "1000 10TH CITPD",
                   "1000 10TH PFT LAB",
                   "1000 10TH AVE PSYCHIATRY")
total_rooms <- 58 # Excludes 4 of 61 exam rooms occupied by Radiation Oncology on Lower Level 
```


```{r Space Committee Assessment Analysis, echo = FALSE, warning = FALSE, message = FALSE}

# Processed Util Data for Analysis ---------------------------------------------
util_data <- util_data %>%
  mutate(exclude_visits = case_when(str_detect(PRC_NAME, visits_exclude) ~ "Exclude",
                                    str_detect(VISIT_TYPE, visit_types_exclude) ~ "Exclude",
                                    TRUE ~ "")) %>%
  filter(exclude_visits != "Exclude") %>%
  filter(DEPARTMENT %!in% depts_exclude) %>%
  filter(APPT_DATE_YEAR < as.Date("2024-01-01")) %>%
  mutate(APPT_MONTH = format(as.Date(APPT_DATE_YEAR), "%b"))


# List of departments filtered -------------------------------------------------
depts_filtered <- util_data %>%
  group_by(DEPARTMENT_OLD, VISIT_METHOD) %>%
  summarise(total = n()) %>%
  pivot_wider(names_from = VISIT_METHOD,
              values_from = total,
              values_fill = 0) %>%
  mutate(specialty = "NA",
         floor = "NA") 


# Average In-PErson Encounters per Day -----------------------------------------
avg_visits_day <- util_data %>%
  filter(APPT_YEAR == 2023) %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(APPT_MONTH = month(APPT_DATE_YEAR)) %>%
  # filter(APPT_MONTH < 11) %>%
  group_by(APPT_YEAR, APPT_DATE_YEAR) %>%
  summarise(total = n()) %>%
  group_by(APPT_YEAR) %>%
  summarise(avg_visits = mean(total)) 

# Average In-PErson Encounters per Day by Department -----------------------------
avg_visits_dept <- util_data %>%
  filter(APPT_YEAR == 2023) %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(APPT_MONTH = month(APPT_DATE_YEAR)) %>%
  # filter(APPT_MONTH < 11) %>%
  group_by(DEPARTMENT_OLD, APPT_YEAR, APPT_MONTH_YEAR) %>%
  summarise(total = n()) %>%
  ungroup() %>%
  group_by(APPT_MONTH_YEAR) %>%
  mutate(percent_total = round(total/sum(total),2)) 

# Average Utilization by Month ------------------------------------------------
avg_usage_facility_month <- util_data %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(total_rooms = total_rooms) %>%
  group_by(APPT_MONTH_YEAR) %>%
  mutate(total_days = length(unique(APPT_DATE_YEAR)),
         total_visits = length(unique(PAT_ENC_CSN_ID))) %>%
  group_by(APPT_YEAR, APPT_MONTH_YEAR, APPT_MONTH, total_days, total_rooms, total_visits) %>%
  summarise(total_min = sum(SUM)) %>%
  mutate(avg_visits = round(total_visits/total_days/total_rooms,2),
         avg_util = round(total_min/(total_days*total_rooms*8*60),2)*100) 

# Average Utilization by Year ----------------------------------------------------
avg_usage_facility_year <- util_data %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(total_rooms = total_rooms) %>%
  group_by(APPT_YEAR) %>%
  mutate(total_days = length(unique(APPT_DATE_YEAR)),
         total_visits = length(unique(PAT_ENC_CSN_ID))) %>%
  group_by(APPT_YEAR, total_days, total_visits) %>%
  summarise(total_min = sum(SUM),
            total_rooms = round(mean(unique(total_rooms)),1)) %>%
  mutate(avg_visits = round(total_visits/total_days/total_rooms,2),
         avg_util = round(total_min/(total_days*total_rooms*8*60),2)*100) %>%
  mutate(APPT_MONTH_YEAR = ifelse(APPT_YEAR == 2022, "FY22 Baseline", "FY23 YTD"))


# Utilization YOY Target -------------------------------------------------------
baseline <- round(avg_usage_facility_year[avg_usage_facility_year$APPT_YEAR=="2022","avg_visits"],2)
target <- round(avg_usage_facility_year[avg_usage_facility_year$APPT_YEAR=="2022","avg_visits"]*1.05,2)
target_10 <- round(avg_usage_facility_year[avg_usage_facility_year$APPT_YEAR=="2022","avg_visits"]*1.1,2)

avg_usage_facility <- bind_rows(avg_usage_facility_month, avg_usage_facility_year)


# Utilization by Day of Week ---------------------------------------------------
avg_visits_dow <- util_data %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(total_rooms = total_rooms) %>%
  group_by(APPT_YEAR, APPT_DAY) %>%
  mutate(total_days = length(unique(APPT_DATE_YEAR)),
         total_visits = length(unique(PAT_ENC_CSN_ID))) %>%
  group_by(APPT_YEAR, APPT_DAY, total_days, total_rooms, total_visits) %>%
  summarise(total_min = sum(SUM)) %>%
  mutate(avg_visits = round(total_visits/total_days/total_rooms,2),
         avg_util = round(total_min/(total_days*total_rooms*8*60),2)*100) %>%
   arrange(match(APPT_DAY, c("MON","TUE","WED","THU","FRI"))) %>%
  arrange(APPT_YEAR)

# Utilization by Hour ----------------------------------------------------------
avg_visits_hour <- util_data %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(total_rooms = total_rooms) %>%
  mutate(APPT_HOUR  = format(strptime(as.ITime(floor_date(APPT_DTTM, "hour")), "%H:%M:%S"),'%H:%M')) %>%
  group_by(APPT_YEAR, APPT_DAY) %>%
  mutate(total_days = length(unique(APPT_DATE_YEAR))) %>%
  group_by(APPT_YEAR, APPT_DAY, APPT_HOUR, total_days, total_rooms) %>%
  summarise(total_visits = length(unique(PAT_ENC_CSN_ID))) %>%
  mutate(avg_visits = round(total_visits/total_days,2)) 


# Graph Output -----------------------------------------------------------------
# Room Usage Trend -------------------------------------------------------------
highchart() %>%
  hc_yAxis_multiples(
    list(title = list(text = "Avg Visits/Room/Day"), lineWidth = 3
         # plotLines = list(list(value = as.numeric(target), color = "red", width = 2, 
         #                       dashStyle = "shortdash",
         #                       label = list(text = "+5% from FY22", style = list(color = "red", fontWeight = "bold"))
         #                       ),
         #                  list(value = as.numeric(target_10), color = "orange", width = 2, 
         #                       dashStyle = "shortdash",
         #                       label = list(text = "+10% from FY22", style = list(color = "orange", fontWeight = "bold"))
         #                       ))
         ),
    list(title = list(text = "% Room Utilization"), min = 0, max = 100, showLastLabel = FALSE, opposite = TRUE)
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = avg_usage_facility_month$APPT_MONTH_YEAR,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Avg Visits/Room/Day",
                data = avg_usage_facility_month$avg_visits,
                type = 'column',
                color= "#a5a7a5",
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_add_series(name = "% Room Utilization",
                data = avg_usage_facility_month$avg_util,
                type = "line", yAxis = 1,
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = "Room Usage Trend", align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("FY22 Baseline = ", as.numeric(baseline)," visits/room/day"
                            ),
  align = "left", style = list(color = "red", fontWeight = "bold", fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
  

# Turns per Room Trend ---------------------------------------------------------
highchart() %>%
  hc_add_series(type = "line", data = avg_usage_facility_month, hcaes(x = APPT_MONTH, y = avg_visits, group = APPT_YEAR), 
                dataLabels = list(
                  enabled = TRUE)) %>%
  hc_xAxis(title = list(text = ""),
           categories = avg_usage_facility_month$APPT_MONTH
           # type = "datetime",
           # labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_yAxis(title = list(text = "Avg Visits/Room/Day"), 
           min = 0, lineWidth = 3,
           datalabels = list(enabled = TRUE, format = "{point.avg_visits}")
           # plotLines = list(list(value = as.numeric(target), color = "red", width = 2, 
           #                       dashStyle = "shortdash"
           #                       # label = list(text = "Visits/Room/Day Target (+5%)", style = list(color = "red", fontWeight = "bold"))
           #                     ))
           ) %>%
  hc_colors(c("#d80b8c","#a5a7a5")) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = "Room Usage Trend", align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("FY22 Baseline = ", as.numeric(baseline)," visits/room/day"
                            ),
  align = "left", style = list(color = "red", fontWeight = "bold", fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")


# Room Occupancy Trend ---------------------------------------------------------  
highchart() %>%
  hc_add_series(type = "line", data = avg_usage_facility_month, hcaes(x = APPT_MONTH, y = avg_util, group = APPT_YEAR), 
                dataLabels = list(
                  enabled = TRUE,
                  format = "{point.avg_util}%")) %>%
  hc_xAxis(title = list(text = ""),
           categories = avg_usage_facility_month$APPT_MONTH
           # type = "datetime",
           # labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_yAxis(title = list(text = "Avg % Utilization"), 
           min = 0, max = 100, lineWidth = 3,
           datalabels = list(enabled = TRUE, format = "{point.avg_util}%"),
           plotLines = list(list(value = 85, color = "red", width = 2, 
                                 dashStyle = "shortdash"
                                 # label = list(text = "Visits/Room/Day Target (+5%)", style = list(color = "red", fontWeight = "bold"))
                               ))) %>%
  hc_colors(c("#d80b8c","#a5a7a5")) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = "Room Usage Trend", align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("Avg Room Utilization Target = 85%"),
              align = "left", style = list(color = "red", fontWeight = "bold", fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")


# Visits/Room/Day YOY vs. Target --------------------------------------------  
highchart() %>%
  hc_yAxis(
    title = list(text = "Avg Visits/Room/Day"), 
    lineWidth = 3,
plotLines = list(list(value = as.numeric(target), color = "red", width = 2,
                      dashStyle = "shortdash",
                      label = list(text = "+5% from FY22", style = list(color = "red", fontWeight = "bold"))
                      )
                 # list(value = as.numeric(target_10), color = "orange", width = 2,
                 #      dashStyle = "shortdash",
                 #      label = list(text = "+10% from FY22", style = list(color = "orange", fontWeight = "bold"))
                 #      )
                 )
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = avg_usage_facility_year$APPT_MONTH_YEAR,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "Avg Visits/Room/Day",
                data = avg_usage_facility_year$avg_visits,
                type = 'column',
                color= "#a5a7a5",
                dataLabels = list(enabled = TRUE, format='{point.y}')) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = "Visits/Room/Day YOY vs. Target", align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("+5% from FY22 Baseline = ", as.numeric(target)),
              align = "left", style = list(color = "red", fontWeight = "bold", fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")
  


# % Room Utilization YOY vs. Target --------------------------------------------  
highchart() %>%
  hc_yAxis(
    title = list(text = "% Room Utilization"), 
    min = 0, max = 100, 
    showLastLabel = FALSE,
    plotLines = list(list(value = 85, color = "red", width = 2,
                          dashStyle = "shortdash",
                          label = list(text = "Target", style = list(color = "red", fontWeight = "bold"))
                          ))
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = avg_usage_facility_year$APPT_MONTH_YEAR,
           type = "datetime",
           labels = list(format = '{value:%m/%d}')
           # dateTimeLabelFormats = list(month = '%Y-%m')
           ) %>%
  hc_add_series(name = "% Room Utilization",
                data = avg_usage_facility_year$avg_util,
                type = "line", 
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE, format='{point.y}%'))  %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = "% Room Utilization YOY vs. Target", align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("FY23 % Room Utilization: 85%"),
              align = "left", style = list(color = "red", fontWeight = "bold", fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")



# Visits/Room/Day by Day Of Week -----------------------------------------------
highchart() %>%
  hc_yAxis(
    title = list(text = "Avg Visits/Room/Day"), 
    lineWidth = 3,
    plotLines = list(list(value = as.numeric(target), color = "red", width = 2,
                      dashStyle = "shortdash", 
                      label = list(text = "+5% from FY22", align = "right", style = list(color = "red", fontWeight = "bold"))
                      )
                 # list(value = as.numeric(target_10), color = "orange", width = 2,
                 #      dashStyle = "shortdash",
                 #      label = list(text = "+10% from FY22", style = list(color = "orange", fontWeight = "bold"))
                 #      )
                 )
  ) %>%
  hc_xAxis(title = list(text = ""),
           categories = avg_visits_dow$APPT_DAY
           ) %>%
  hc_add_series(data = avg_visits_dow %>% filter(APPT_YEAR == 2022), type = 'column', hcaes(x = APPT_DAY, y = avg_visits, group = APPT_YEAR),
                color='#a5a7a5',
                lineColor='#a5a7a5',
                dataLabels = list(enabled = TRUE)) %>% 
  hc_add_series(data = avg_visits_dow %>% filter(APPT_YEAR == 2023), type = 'column', hcaes(x = APPT_DAY, y = avg_visits, group = APPT_YEAR),
                color='#d80b8c',
                lineColor='#d80b8c',
                dataLabels = list(enabled = TRUE)) %>%
  hc_legend(align = "left", verticalAlign = "top", itemStyle = list(fontFamily ='Calibri',color ='black', fontSize = "14px")) %>%
  hc_title(text = "Avg Visits/Room/Day by Day of Week", align = "left", style = list(fontWeight = 'bold', fontSize = "22px", fontFamily = "Calibri")) %>%
  hc_subtitle(text = paste0("FY22 Baseline = ", as.numeric(baseline)," visits/room/day"
                            ),
  align = "left", style = list(color = "red", fontWeight = "bold", fontFace = "italic", fontSize = "16px", fontFamily = "Calibri")) %>%
  hc_tooltip(shared = TRUE, borderColor = "black")

```


```{r Provider Analysis, echo = FALSE, warning = FALSE, message = FALSE}

# Visits/Room/Day by Provider --------------------------------------------------
visits_provider <- util_data %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(APPT_MONTH = month(APPT_DATE_YEAR)) %>%
  mutate(APPT_HOUR = format(strptime(as.ITime(floor_date(APPT_START, "hour")), "%H:%M:%S"),'%H:%M')) %>%
  mutate(session = ifelse(APPT_HOUR<12, "AM","PM")) %>%
  group_by(APPT_YEAR, APPT_MONTH, APPT_DATE_YEAR, APPT_DAY, session, CAMPUS_SPECIALTY, DEPARTMENT, PROVIDER, prov_type) %>%
  summarise(total_visits = length(unique(PAT_ENC_CSN_ID)),
            total_min = sum(SUM))


require(openxlsx)
write.xlsx(visits_provider, "1090 Amst Ave Urology Visits by Provider.xlsx")


# Avg Visits/Room/Day by Month -------------------------------------------------
avg_usage_dept <- util_data %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  mutate(APPT_HOUR = format(strptime(as.ITime(floor_date(APPT_START, "hour")), "%H:%M:%S"),'%H:%M')) %>%
  mutate(session = ifelse(APPT_HOUR<12, "AM","PM")) %>%
  group_by(APPT_YEAR, APPT_MONTH_YEAR, APPT_DATE_YEAR, APPT_DAY, session, DEPARTMENT, PROVIDER) %>%
  summarise(total_visits = length(unique(PAT_ENC_CSN_ID)),
            total_min = sum(SUM))


write.xlsx(avg_usage_dept, "Room Usage Analysis_85TH_Aug23.xlsx")


avg_usage_dept_session <- util_data %>%
  filter(APPT_DAY %!in% c("SAT","SUN")) %>%
  pivot_longer(H_07_00:H_20_00,
               names_to = "hour",
               values_to = "roomed_min") %>%
  mutate(hour = as.numeric(substr(hour, start = 3, stop = 4))) %>%
  mutate(session = ifelse(hour<12, "AM","PM")) %>%
  dplyr::select(APPT_YEAR, APPT_MONTH_YEAR, APPT_DATE_YEAR, APPT_DAY, DEPARTMENT, PROVIDER, RESOURCES, hour, roomed_min) %>%
  mutate(hour = as.character(hour)) %>%
  group_by(APPT_YEAR, APPT_MONTH_YEAR, APPT_DATE_YEAR, APPT_DAY, DEPARTMENT, PROVIDER, RESOURCES, hour) %>%
  summarise_if(is.numeric, sum, na.rm = TRUE)

```
